### 2019-09-04 experiments.tex
result

Table \ref{tab:overviewexp} shows a summary of our experimental
results.  In all cases, our approach was able to detect interesting
nondeterminism.  The overhead on testing imposed by nondeterminism
checks varied considerably, but in the worst case did not double the
average cost of each action, and thus never halved the amount of
testing performed.  Test reduction always reduced the size of
generated tests by 90\% or more, thus showing that effective reduction
has a large payoff.

\begin{table}
\centering
\begin{tabular}{l|l|r|r|l}
Subject & Detection & Overhead & Reduction & Reduction time \\
\hline
Parallel Sort & Yes (see below) & $\sim$40\% & & $\sim$2 minutes\\
{\tt redis-py} & Yes (see below) & $\sim$20\% & $\sim$95\% & $\sim$10 minutes\\
{\tt datarray} & Yes (see below) & $\sim$93\% & $\sim$90\% & $\sim$92
  seconds\\
{\tt pyfakefs} & Yes (see below) & $\sim$8\% & $\sim$99\% & $\sim$1 second  \\
\end{tabular}
\caption{Overview of experimental results}
\label{tab:overviewexp}
\end{table}

>>>>

Table \ref{tab:overviewexp} shows a summary of our experimental
results.  In all cases, our approach was able to detect interesting
nondeterminism.  The overhead on testing imposed by nondeterminism
checks varied considerably, but in the worst case did not double the
average cost of each action, and thus never halved the amount of
testing performed.  Test reduction always reduced the size of
generated tests by 85\% or more, in less than 15 minutes, thus showing that effective reduction
has a large payoff at an acceptable price.

\begin{table}
\centering
\begin{tabular}{l|l|r|r|l}
Subject & Detection & Overhead & Reduction & Reduction time \\
\hline
Parallel Sort & Yes (see below) & $\sim$40\% & $\sim$85\% & $\sim$2 minutes\\
{\tt redis-py} & Yes (see below) & $\sim$20\% & $\sim$95\% & $\sim$10 minutes\\
{\tt datarray} & Yes (see below) & $\sim$93\% & $\sim$90\% & $\sim$92
  seconds\\
{\tt pyfakefs} & Yes (see below) & $\sim$8\% & $\sim$99\% & $\sim$1 second  \\
\end{tabular}
\caption{Overview of experimental results}
\label{tab:overviewexp}
\end{table}
